%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{tgpagella} % or any other font family that supports the shape
\usepackage{microtype}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{fontawesome}
\usepackage{svg}

% NEW: Needed for inserting images (SVG, PNG, PDF)
\usepackage{graphicx}

%----------FONT OPTIONS----------
% (Comment out what you aren't using)
\usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% \usepackage{CormorantGaramond}
% \usepackage{charter}

\hypersetup{
  colorlinks=true,
  linkcolor=blue, % color of internal links
  urlcolor=blue   % color of external links
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\setlength{\footskip}{4.08003pt}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}
\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{
\begin{itemize}[leftmargin=0.15in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{
\end{itemize}}
\newcommand{\resumeItemListStart}{
\begin{itemize}}
    \newcommand{\resumeItemListEnd}{
\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Logan Travis} \\ \vspace{1pt}
  \small
  \href{mailto:lgntravis@gmail.com}{\underline{lgntravis@gmail.com}} $|$
  \href{https://www.linkedin.com/in/logantravis/}{\underline{LinkedIn}} $|$
  \href{https://github.com/Logan9312}{\underline{GitHub}} $|$
  \href{https://ltravis.ca/}{\underline{Portfolio}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Alberta}{Edmonton, Alberta}
{Bachelor of Science in Computer Science with Specialization}{September 2020 - December 2025}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Jobber}{May 2025 - Present}
{Software Engineer}{Edmonton, AB}
\resumeItemListStart
\resumeItem{Building full-stack features in \textbf{Ruby on Rails}, \textbf{TypeScript}, and \textbf{GraphQL} for a platform serving 100k+ businesses.}
\resumeItem{Optimized \textbf{Searchkick} reindexing for integration with \textbf{The Home Depot} (4M+ products at 2,000+ stores).}
\resumeItem{Reduced reindexing time from over 6 hours to 45 minutes by researching indexing strategies via \textbf{Sidekiq}.}
\resumeItem{Migrated \textbf{React islands} in \textbf{Rails} views to a \textbf{React SPA}, improving maintainability and developer velocity.}
\resumeItem{Implemented cross-team refactors across quotes, scheduling, and other external domains, coordinating with stakeholders on technical approach within a large monolith.}
\resumeItem{Prototyped and added \textbf{Apollo} caching with useFragment hooks to get around technical limitations with asynchronous GraphQL queries, allowing hydration of data from third party API application after initial payload.}

\resumeItemListEnd

\resumeSubheading
{Activision}{May 2024 - May 2025}
{Software Developer Intern}{Vancouver, BC}
\resumeItemListStart
\resumeItem{Built \textbf{Call of Duty: Black Ops 6} leaderboard UI running in an in-game browser, a stripped-down \textbf{React} runtime on PS5/Xbox constrained by leftover game memory, requiring strict optimization to prevent crashes.}
\resumeItem{Engineered performant components for in-game leaderboards and combat record under hardware memory limits using memoization, lazy loading, CDN asset caching, and \textbf{Jenkins} workflows for asset and test-build deploys.}
\resumeItem{Designed and shipped a Discord bot from scratch using \textbf{Java/Discord4J} as an intern-only project providing real-time player stats to the community. Involved rate-limiting and scaling shards for a server with over \textbf{650k users}, and prototyping \textbf{distributed sharding configurations}.}
\resumeItem{Refactored legacy code from \textbf{Modern Warfare 3} to improve maintainability and performance.}
\resumeItem{Maintained code quality with \textbf{Jest} unit testing and snapshot tests across all UI components improving confidence in complex refactors for localization text.}
\resumeItem{Solely owned multiple features including the \textbf{Top 250 Leaderboards} and \textbf{Cod League Hub} for ranked play.}

\resumeItemListEnd

\resumeSubheading
{Freelance}{May 2023 - May 2024}
{Full-Stack Developer}{Remote}
\resumeItemListStart
\resumeItem{Built an e-commerce platform (\href{https://shop.vanquished.gg}{shop.vanquished.gg}) for \textbf{8,000+ users} using \textbf{SvelteKit}, \textbf{Go}, and \textbf{PostgreSQL}.}
\resumeItem{Integrated \textbf{Stripe} payments and \textbf{Discord OAuth} for virtual currency system with real-time purchase tracking.}
\resumeItem{Developed one-off applications for multiple clients using \textbf{Go} and \textbf{PostgreSQL} with auth and payment integrations.}
\resumeItem{Refactored legacy \textbf{Python} projects for clients to improve stability and performance, and resolve memory leaks.}
\resumeItemListEnd

\resumeSubheading
{Alberta Chambers of Commerce}{October 2021 - May 2024}
{Chamber Platform Coordinator}{Edmonton, AB}
\resumeItemListStart
\resumeItem{Supported the Shop Local Chamber Market and a CRM platform for local Chambers of Commerce in Alberta.}
\resumeItem{Developed automation scripts for survey aggregation with \textbf{Go}, collecting data from province-wide responses.}
\resumeItem{Worked with developers to beta test platform features and provide feedback from business owners.}
\resumeItem{Supported the onboarding and technical support of businesses across Alberta to a CRM platform and online marketplace.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Gazprea Compiler} $|$ \emph{C++, LLVM, MLIR, ANTLR4} $|$ \href{https://cmput415.github.io/415-docs/gazprea/}{Specs}}{}
\resumeItemListStart
\resumeItem{Built a full \textbf{C++} compiler from scratch: lexer/parser (\textbf{ANTLR4}), and code generation targeting \textbf{LLVM IR} via \textbf{MLIR}.}
\resumeItem{Implemented compiler features including functions, loops, conditionals, type inference, and 2D array operations.}
\resumeItem{Set up self-hosted \textbf{GitHub Actions} to run hundreds of tests in parallel for benchmarking and feature coverage.}
\resumeItem{Developed a second smaller compiler from scratch targeting x86, ARM, and RISC-V assembly.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Prize Bot} $|$ \emph{Go, PostgreSQL, AWS, Stripe, SvelteKit} $|$ \href{https://github.com/Logan9312/Prize-Bot-V1}{GitHub} $|$ \href{https://www.prizebot.dev/}{Website}} {}
\resumeItemListStart
\resumeItem{Built and scaled a \textbf{Go} Discord bot to track \textbf{1,000+ servers} and \textbf{380,000+ users} handling auction and giveaway events and prize distribution through automated ticket system.}
\resumeItem{Integrated \textbf{Stripe} for subscription billing and \textbf{PostgreSQL} for persistent data storage.}
\resumeItem{Implemented \textbf{SvelteKit} frontend with support for all existing bot configurations, and new advanced options.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{2D Game Engine} $|$ \emph{C++, OpenGL, SFML}}{}
\resumeItemListStart
\resumeItem{Built a 2D game engine in \textbf{C++} using \textbf{SFML} and \textbf{OpenGL} shaders, designed around ECS architecture.}
\resumeItem{Implemented a physics engine for 2D collisions, movement, gravity, and camera control with animated sprites.}
\resumeItem{Set up self-hosted GitHub Actions to ensure C++ build system compiles consistently across multiple platforms.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Multiplayer Poker Engine} $|$ \emph{Rust, SvelteKit, PostgreSQL} $|$ \href{https://therustykrab.xyz}{Website}} {}
\resumeItemListStart
\resumeItem{Engineered a networked multiplayer poker server in \textbf{Rust} with async game loops via \textbf{Rocket} with \textbf{mongodb}.}
\resumeItem{Implemented multiple poker variants in a \textbf{SvelteKit} frontend with real-time \textbf{websocket} communication.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Rust Arduino Game} $|$ \emph{Rust, Arduino}}{}
\resumeItemListStart
\resumeItem{A 2D two player game in \textbf{Rust} using \textbf{Arduino} with a physical breadboard controller.}
\resumeItem{Used \textbf{Bevy Engine} for game logic frontend, communicating through websockets from the Rust backend.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{ServerSearch} $|$ \emph{Go, PostgreSQL, Next.js, React} $|$ \href{https://serversearch.xyz/}{Website}}{}
\resumeItemListStart
\resumeItem{An advertisement platform for gameservers developed with \textbf{Go}, \textbf{PostgreSQL}, and \textbf{Next.js}.}
\resumeItem{Supports organizational level user configuration and role hierarchy with authentication via \textbf{Discord OAuth}.}
\resumeItemListEnd

% \resumeProjectHeading
% {\textbf{ScanPal} $|$ \emph{Java, Android Studio, Firebase} $|$ \href{https://www.youtube.com/watch?v=dmA5Nl-ztyk}{Demo}}{}
% \resumeItemListStart
% \resumeItem{Built an Android app for event management, enabling real-time attendance tracking and push notifications.}
% \resumeItem{Designed an interface for seamless communication between the Android client and \textbf{Firebase} backend.}
% \resumeItem{Implemented \textbf{CI/CD} pipelines using GitHub Actions, ensuring code quality and automated testing.}
% \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
    \item{
        \textbf{Languages}{: C/C++, RISC-V/ARM/x86 Assembly, Go, Rust, TypeScript, Python, Java, JavaScript, Ruby, SQL} \\
        \textbf{Frameworks \& Tools}{: LLVM/MLIR, ANTLR4, Jenkins, React, Rails, SvelteKit, Next.js, Rocket, Tailwind, React Native, HTMX, Node.js, GitHub Actions}
    }}
\end{itemize}

%-----------COURSES-----------
\section{Relevant Courses}
\begin{itemize}[leftmargin=0.25in, itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt]
    \small{
    \item \textbf{CMPUT 481}{: Parallel \& Distributed Systems (Go)}
    \item \textbf{COMP 466}{: Advanced Web Technologies (PHP, XML, C\#)}
    \item \textbf{COMP 444}{: Embedded \& Robotic Programming (Rust)}
    \item \textbf{CMPUT 429}{: Systems \& Architecture (Python, gem5)}
    \item \textbf{ECE 421}{: Exploring Software Development (Rust, MongoDB, SvelteKit, TypeScript)}
    \item \textbf{CMPUT 415}{: Compiler Design (C++, LLVM/MLIR, ANTLR4)}
    \item \textbf{CMPUT 379}{: Operating Systems (C)}
    \item \textbf{COMP 378}{: Database Management (SQL)}
    \item \textbf{CMPUT 365}{: Reinforcement Learning}
    \item \textbf{CMPUT 350}{: Advanced Games Programming (C++)}
    \item \textbf{COMP 348}{: Network Programming (Java)}
    \item \textbf{CMPUT 333}{: Security in a Networked World (Python)}
    \item \textbf{CMPUT 303}{: Algorithmics in Practice (Go, Rust)}
    \item \textbf{CMPUT 301}{: Software Engineering (Java)}
    \item \textbf{CMPUT 267}{: Machine Learning (Julia, Python)}
    \item \textbf{CMPUT 261}{: Artificial Intelligence (Python)}
    \item \textbf{CMPUT 229}{: Computer Organization/Architecture I (RISC-V)}
    % \item \textbf{CMPUT 204}{: Algorithms I}
    % \item \textbf{CMPUT 201}{: Practical Programming Methodology (C)}
    }
\end{itemize}

\end{document}
